Untitled

### 2023-09-05 code/analysis_Redo.Rmd
Early vs later competitive shocks

>>>>

## Early vs Late competitors (pre-post ACA?)

df.ppACA <- df.core2 %>% 
  mutate(EarlyLate = ifelse(Att == 0, 0, 
                     ifelse(Att %in% c(2012:2014), 1,# 2))) 
                     ifelse(Att %in% c(2015:2017), 2, 3))))
  #filter(Att %in% c(0, 2016:2021) & Year %in% c(2014:2021)) %>% 
  #filter(Att %in% c(0, 2012:2015) & Year %in% c(2010:2018)) %>%

did.ppACA <- c(0, 0, 0, 0)
for (i in 1:3){
for (j in 10:12){

  df.temp <- df.ppACA[,c(1:9, j, 13:ncol(df.ppACA))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(EarlyLate %in% c(0, i)) , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.ppACA <- rbind(did.ppACA, outcomes$coeftable)
}
}

did.ppACA <- did.ppACA[-1,]
rownames(did.ppACA) <- NULL

data.frame(Subset = sort(rep(1:3, 3)),
      Outcome = rep(c("Total","Quality","Financial"), 3),
      Estimate = as.numeric(did.ppACA[,1]), 
      SD = as.numeric(did.ppACA[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",liquid=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by early vs late adopters")
